### 2025-01-02 preliminaries.tex
Minor modified Preliminaries chapter

HOL includes the constant \(Type\_Definition\), which defines new types as bijections of subsets of existing types:
    \item \textbf{Type Definition \(Type\_Definition\)}
    \begin{itemize}
        \item Rule
        \item This process is automated by the HOL Datatype package, simplifying the creation of new types.

@@

An equivalent definition of \(\sigma\)-algebra is also provided in HOL4 making their construction flexible:
\[
\text{SIGMA\_ALGEBRA\_ALT\_SPACE}:\
\]

@@

\end{enumerate}
The Borel \(\sigma\)-algebra is also important in the definition of measurable functions and measurable spaces in analysis.

@@

>>>>

HOL includes the constant \(Type\_Definition\), which defines new types as bijections of subsets of existing types:
    \item \textbf{Type Definition \(Type\_Definition\)}
    \begin{itemize}
        \item Rule
          \begin{hol}
\begin{verbatim}
  |- TYPE_DEFINITION (P:'a->bool) (rep:'b->'a) =
  (!x' x''. (rep x' = rep x'') ==> (x' = x'')) /\
  (!x. P x = (?x'. x = rep x'))
\end{verbatim}
          \end{hol}
        \item This process is automated by the HOL Datatype package, simplifying the creation of new types.

@@

An equivalent definition of \(\sigma\)-algebra is also provided in HOL4 making their construction flexible:
\begin{hol}
  \begin{alltt}
    SIGMA_ALGEBRA_ALT_SPACE
    \(\!\!\!{\turn}\!\!\!\!\) \(\forall\)a. sigma_algebra a \({\Leftrightarrow}\)
    subset_class (space a) (subsets a) \(\land\) space a \(\in\) subsets a \(\land\)
    (\(\forall\)s. s \(\in\) subsets a \(\Rightarrow\) space a DIFF s \(\in\) subsets a) \(\land\)
    \(\forall\)f. f \(\in\) (\(\mathbb{U}\)(:num) \(\to\) subsets a) \(\Rightarrow\)
    BIGUNION (IMAGE f \(\mathbb{U}\)(:num)) \(\in\) subsets a
  \end{alltt}
\end{hol}

@@

   \begin{hol}
     \begin{alltt}
   right_open_interval
   \(\!\!\!{\turn}\!\!\!\!\) \(\forall\)a b. right_open_interval a b = \{x | a \(\le\) x \(\land\) x < b\}

   right_open_intervals
   \(\!\!\!{\turn}\!\!\!\!\) right_open_intervals = (\(\mathbb{U}\)(:real),\{right_open_interval a b | T\})
     \end{alltt}
   \end{hol}
   \begin{hol}
     \begin{alltt}
   right_open_intervals_semiring
   \(\!\!\!{\turn}\!\!\!\!\) semiring right_open_intervals

   right_open_intervals_sigma_borel
   \(\!\!\!{\turn}\!\!\!\!\) sigma (space right_open_intervals) (subsets right_open_intervals) =
       borel
     \end{alltt}
   \end{hol}
\end{enumerate}

The Borel \(\sigma\)-algebra is also important in the definition of measurable functions and measurable spaces in analysis.

@@

\begin{hol}
  \begin{alltt}
    measurable_def
    \(\!\!\!{\turn}\!\!\!\!\) \(\forall\)a b.
    measurable a b =
    \{f |
    f \(\in\) (space a \(\to\) space b) \(\land\)
    \(\forall\)s. s \(\in\) subsets b \(\Rightarrow\) PREIMAGE f s \(\cap\) space a \(\in\) subsets a\}
  \end{alltt}
\end{hol}
